Deciphering Mortality in Alberta: A Multifaceted Analysis

### 2024-03-16 outputs/paper/paper.qmd
paper final draft

Data used in this paper was cleaned and processed with the programming language R [@citeR]. Also with support of additional packages in R: `tidyverse` [@citeTidyverse], `ggplot2` [@citeGgplot], `janitor` [@citeJanitor], `readr` [@citeReadr], `knitr` [@citeKnitr], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `tidybayes` [@citeTidybayes], `loo` [@citeLoo].

>>>>

Data used in this paper was cleaned, processed and tested with the programming language R [@citeR]. Also with support of additional packages in R: `tidyverse` [@citeTidyverse], `ggplot2` [@citeGgplot], `janitor` [@citeJanitor], `readr` [@citeReadr], `knitr` [@citeKnitr], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `tidybayes` [@citeTidybayes], `loo` [@citeLoo], `testthat` [@citeTestthat].
